GEE models

### 2017-10-15 doc/manuscript.Rmd
revised contrib section

The authors had the following responsibility: LWJ conducted research, analysed
data, and wrote the paper; RR, ZL, and SBH designed research, conducted
research, and provided essential materials (infrastructure and clinical
resources); RR, SBH, RPB, and AG provided intellectual feedback on the
paper; RPB conducted research, provided essential reagents and materials; AJH
designed research, assisted with interpretation, and provided intellectual
feedback on all versions of the paper; LWJ and AJH had primary responsibility
for final content and are the guarantors of this work. All authors read and
approved the final manuscript.

>>>>

The authors had the following responsibility: LWJ analysed and interpreted the
data and drafted the article; RR and SBH contributed to the conception and
design and revised the article on intellectual content; ZL acquired the data and
revised the article on intellectual content; AG assisted with interpretation of
the data and revised the article on intellectual content; AJH and RPB
substantially contributed to the study conception and design, assisted with
interpretation of the data, and revised the article on intellectual content. All
authors read and approved the final version. LWJ and AJH have primary
responsibility for final content and are the guarantors of this work.
